\documentclass[a4paper,10pt]{letter}

\usepackage[margin=1cm]{geometry}
\usepackage{tabularx}
\usepackage{listings}
\usepackage{longtable}
\usepackage{hyperref}

\pagenumbering{gobble}
\hyphenpenalty=10000

\begin{document}



\LARGE
\textbf{Ash Bellett}\\
\large
\newline
\begin{tabular}{ @{} p{2cm} p{8cm} p{2cm} l }
\textbf{Location} & Melbourne, Australia & \textbf{LinkedIn} & \href{https://www.linkedin.com/in/ashbellett}{ashbellett} \\ 
\textbf{Phone} & \href{tel:61468620576}{+61 468 620 576} & \textbf{GitHub} & \href{https://www.github.com/ashbellett}{ashbellett} \\
\textbf{Email} & \href{mailto:ash.bellett.ab@gmail.com}{ash.bellett.ab@gmail.com} & \textbf{Kaggle} & \href{https://www.kaggle.com/ashbellett}{ashbellett} 
\end{tabular}

Data science and software engineering professional with 3 years of technical consulting experience in analytics, artificial intelligence and application development.

\begin{longtable}{ @{} p{2.5cm} p{12cm} r }
\hline \\
\large
\textbf{Experience} & \textbf{IBM} & \normalsize Jun. 2019 -- present \\
 & \textbf{Senior Technical Consultant} & \\
\large
 & Developed an advanced analytics platform using Node.js, Python and Tableau to increase containment of a consumer-facing virtual assistant for a large telecommunications client. & \\
 & Created a cognitive search and research tool using Typescript, Node.js, React and various IBM Watson APIs to assist knowledge transfer between electrical engineers for a large energy client. & \\
 & Built a cognitive search-enabled virtual assistant using Typescript, Node.js, the Slack API and various IBM Watson APIs to assist drivers understand complex road rules for a Defence department. & \\
 & & \\
\large
 & \textbf{IBM} & \normalsize Feb. 2018 -- Jun. 2019 \\
 & \textbf{Technical Consultant} & \\
\large
 & Contributed to a large case management system using Javascript and Python to assist knowledge workers with processing complex workflows for a large government client. & \\
 & Collaborated with IBM Research to propose an NLP solution that can assess whether the financial advice given by banks supports customers' goals for a large financial services client. & \\
 & Designed an internal virtual assistant application to help call centre staff respond to customer policy questions for a large insurance client. & \\
 & & \\
\large
 & \textbf{IBM Graduate Network - Australia and New Zealand} & \normalsize Jul. 2018 -- Jul. 2019 \\
 & \textbf{Chief Digital Officer} & \\
\large
 & Designed, built and deployed the IBM Graduate Network web application using Node.js, HTML and CSS to transition from text-based newsletter content to interactive media. & \\
 & Recorded, edited and published a video interview series with IBM leaders to share their experiences with the IBM graduate community. & \\
 & Shaped the digital strategy of the IBM Graduate Network by advocating adoption of various social channels like Slack and web-based video messaging. & \\
 & & \\
\large
 & \textbf{Mingara Australasia} & \normalsize Nov. 2016 -- Nov. 2017 \\
 & \textbf{Data Analyst} & \\
\large
 & Performed geospatial data analysis using GIS software and SQL to inform the design of a large wireless communications network for a state government client. & \\
 & Presented exploratory data analysis of census data to justify design decisions for emergency services clients. & \\
 & Carried out statistical analysis using Excel and VBA to support presentations with various stakeholders and clients. & \\
 & & \\
\newpage
\hline \\
\large
\textbf{Education} & \textbf{Monash University} & \normalsize Feb. 2013 -- Nov. 2017 \\
 & \textbf{Bachelor of Engineering (with Honours)} & \\
 & \textbf{Electrical and Computer Systems} & \\
\large
 & Honours Thesis: \textit{``Optimisation of Relay-Assisted Wireless Systems in Quasi-Static Environments using Ray Tracing"}. & \\
 & Published a conference paper at the IEEE ITNAC 2017 conference. & \\
 & Completed a Masters unit on Wireless Communications which covered advanced topics in signal processing, probability and information theory. Received a High Distinction grade. & \\
 & \\

\hline \\
\textbf{Projects} & \textbf{Playing video games with deep reinforcement learning} & \\
 & \texttt{python}, \texttt{gym}, \texttt{tensorflow} & \\
 & Implemented a Deep Q-Network algorithm to land a 2D rocket on the surface of a moon using OpenAI's Gym simulation environment. Currently ranked 3rd on the OpenAI GitHub leaderboard for the Lunar Lander environment. & \\
 & & \\
 & \textbf{3D simulation with objects, physics and lighting} & \\
 & \texttt{javascript}, \texttt{three.js} & \\
 & Built a 3D world using the Three.js library with programmatic objects, physics, lighting and camera configurations. Features include object dynamics, object collisions and object destruction. & \\
 & & \\
 & \textbf{Portfolio optimisation using historical stock price data} & \\
 & \texttt{python}, \texttt{numpy}, \texttt{pandas}, \texttt{scipy}, \texttt{matplotlib}, \texttt{cvxpy} & \\
 & Framed stock selection as a mixed-integer quadratic programming problem and solved it using a convex optimisation library. Identified stocks to create a portfolio with highest return and lowest variance from ASX historical stock price data. & \\
 & & \\
 & \textbf{Dating analysis and predictive modelling} & \\
 & \texttt{python}, \texttt{numpy}, \texttt{pandas}, \texttt{scipy}, \texttt{matplotlib}, \texttt{scikit-learn} & \\
 & Built a machine learning model to determine whether a partner will match with their date based on dating preferences and personal background information. Included exploratory data analysis, feature engineering, hyperparameter tuning, model ensembling and model selection. & \\
 & & \\

\hline \\
\large
\textbf{Awards} & \textbf{IBM Inferno Award} & \normalsize 2019 \\
& Awarded to the 3 highest achieving graduates in their first year at IBM. & \\
 & \textbf{IBM Think Prize} & \normalsize 2019 \\
& Attended the IBM Think technology conference in San Francisco for demonstrating high impact to clients. & \\
 & \textbf{4 $\times$ IBM Manager's Choice Awards} & \normalsize 2018 \\
& Awarded to employees who exemplify IBM's values and accomplish project success. & \\
 & \textbf{Monash Dean's Honours List} & \normalsize 2017 \\
& Awarded to students who achieved an average of 80\% or above during the academic year. & \\
\end{longtable}

\end{document}
