\documentclass{letter}

\usepackage[utf8]{inputenc}
\usepackage[a4paper,total={19cm,27.7cm}]{geometry}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{array}
\usepackage{tabularx}

\linespread{1.1}
\setlength{\arrayrulewidth}{1mm}

\begin{document}

	\pagenumbering{gobble}
	\centering
	\rule{\textwidth}{2mm}
	\LARGE
	\textbf{Ash Bellett}\\
	\large
	\begin{center}
	\begin{tabularx}{\textwidth}{X | X}
	\hline
	 & \\
	\Large \textbf{Relevant Experience} & \Large \textbf{Notable Projects}\\
	 & \\
	\large \textbf{IBM}\hfill Feb. `18 -- Feb. `20 & \textbf{Data science pipeline portfolio} \\
	\textbf{Graduate Consultant} & Developed basic components of a data science \\
	Part of IBM`s `Consulting by Degrees' graduate & pipeline including data mining via web scraping, \\
	program. & data wrangling in R, data analysis using machine\\
	 & learning and visualisation using Python.\\
	\textbf{Mingara Australasia} \hfill Nov. `16 -- Nov. `17 & \\
	\textbf{Project Officer} & \textbf{Web development using the Django}\\
	Used MapInfo and SQL to transform raw, & \textbf{framework}\\
	geospatial data into visual maps for clients. & Designed a simple intranet website using Python,\\
	 & HTML and the Bootstrap CSS framework.\\
	\textbf{Robogals Monash}\hfill Jul. `16 -- Jul. `17 & Database was managed using MySQL.\\
	\textbf{President} & Deployed using AWS Elastic Beanstalk.\\
	Lead a team of students who organised robotics & \\
	workshops for children and young adults. & \textbf{Wireless channel modelling and}\\
	 & \textbf{optimisation using ray tracing}\\
	\textbf{MYER} \hfill Oct. `15 -- Oct. `16 & Developed a ray tracing algorithm for wireless\\
	\textbf{Sales Assistant} & signal propagation using C and MATLAB.\\
	Engaged customers by tailoring services using & Validated the simulation results using data from\\
	MYER's interaction strategy. & software-defined radio measurements.\\
	 & \\
	 \cline{1-1}
	 \cline{2-2}
	 & \\
	\Large \textbf{Academic Background} & \Large \textbf{Online Courses}\\
	 & \\
	\textbf{Monash University} \hfill Feb. `13 -- Nov. `17 & \textbf{Computing for Data Analysis}\\
	\textbf{Bachelor of Engineering} (Honours) & \textbf{Georgia Institute of Technology}\\
	Electrical and Computer Systems & Covered the basic processes of data analysis\\
	 & including data collection, pre-processing, storage,\\
	Published a conference paper on wireless channel & analysis and visualisation.\\
	modelling at the 27th IEEE ITNAC. & \\
	 & \textbf{Machine Learning for Data Science}\\
	Completed a Masters unit on Wireless & \textbf{Columbia University}\\
	Communications which covered advanced topics & Introduced machine learning principles such as\\
	in probability and information theory. & algorithms, classifiers, dimensionality reduction,\\
	 & state vector machines and neural networks.\\
	\cline{1-1}
	 & \\
	\Large \textbf{Technical Competencies} & \textbf{The Analytics Edge}\\
	 & \textbf{Massachusetts Institute of Technology}\\
	\textbf{Languages:} Python, C, R, SQL, Unix shell & Covered analytics methods including R\\
	\textbf{Tools:} Microsoft Office, MapInfo, Git & programming, linear and logistic regression, trees\\ 
	\textbf{Packages:} Pandas, Scikit-Learn, Matlibplot & and forests, clustering and optimisation.\\
	 & \\
	\cline{1-1}
	\cline{2-2}
	\end{tabularx}
	\end{center}
	\begin{center}
	\begin{tabular}{cc}
	\href{tel:61468620576}{0468 620 576} & \href{https://www.linkedin.com/in/ash-bellett-07739695}{linkedin.com/in/ash-bellett-07739695}\\
	\href{mailto:ash.bellett.ab@gmail.com}{ash.bellett.ab@gmail.com} & \href{https://www.github.com/ashbellett}{github.com/ashbellett}
	\end{tabular}
	\end{center}
	\rule{\textwidth}{2mm}
	
\end{document}